---
title: "Quiz"
author: "Anish Mohan"
date: "February 17, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
x = c(5,25,3,-34,33, 89, 7, 1, 90, 66)
```

Length of the vector x
```{r}
```

### Vector Operations


Insert 199 in 3rd position
Declare a new vector with values 2,4
Declare a new empty vector of length 2 elements and set their values are 2,4 
  # http://stackoverflow.com/questions/22104774/how-to-initialize-a-vector-with-fixed-length-in-r
Declare 2 vectors of length 2 and get them as a matrix; 2 vectors form columns
Declare 2 vectors of length 2 and get them as a matrix; 2 vectors form rows
Declare 2 vectors of length 2 and get them as a matrix; 2 vectors form rows; Increment as follows (1,1) by 1, (1,2) by 2, (2,1) by 3 and (2,2) by 4
  #increment by adding a new array or another method to add a ?
Declare a matrix with rbind c(1,1) 3 times; now add c(1,5) to it, what is the expected result?
  
Declare a new matrix with data = c(11,22,33,44)
  # what happens when you do not set nrow.

Add, Subtract, Divide, Multiply and Mod the above matrix with c(1,2,2,1)
u = c(22,35, 45) v = c(31, 22, 42); Are each element of u greater than corr element in v


Write a function to consume vector and increment its value by 1, give the sqrt, give the sqr, element multiplication, multiply by itself
Write a function, takes 2 vector arguments, adds them and find the square.
Write a function, takes 1 vector and 1 scalar arguments, adds them and find the square.
print elements if greater than 5
print element if  square of elements is greater than 10
print indices of elements greater than 25
if element of x are greater than 25 assign them to be -1; no for loop
What is the differnece between using subset() vs normal filtering x[x>2]


### Vector Indexing
print last element
print all elements except first element
print all element except last element
print 1st and 3rd element
print odd numbered elements
What is difference between for i in k+5 vs for i in (k+25) ?

### Sequence
Sequence from 1:50
Sequence from 1:50, skip 5
Sequence from 1:50 with length 15

In for loop : for(i in 1:length(x)) what happens if x =NULL

### Creating repeated vectors
repeated vector of c(1,2) with total length = 30
repeated vector of c(1,2,3,4,5) with total length = 30; write compact
repeated vector of c(1,2,3,4,5) where each element is repeated thrice

### Use any() and all()
For x declared above (x = c(5,25,3,-34,33, 89, 7, 1, 90, 66)) are all elements greater than 7
For x declared above (x = c(5,25,3,-34,33, 89, 7, 1, 90, 66)) are any elements greater than 7

### Code workout
Given a series of 1s and 0s find indices where runs of 1s start; runs have to be greater than1
Time series data: 1 = rain, 0 = no rain. Predict rain for tomorrow, based on majority for last k days and compare results
Do the timeseries example and use cumsum() function there

### Using simply apply or sapply()
Function: Input a vector, output = vector and its square; write with and without sapply; return can be a matrix

### NA & NULL difference
Is mode of NA numeric or character or something else
What is length of NA and NULL
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


### ifelse
x = 1:10; print elements divisible by 2; use ifelse
x = 1:10, if number less than 5 cube it else square it

### Code Work out Example:
Two series given; find out the avg number of times they increase or decrease together
Same as above; checks if using diff can simplify the code
Now can you right this in 1 line (Hint use diff and sign function)

g = c("M","F","F","I","M","M","F"); assign locations of M to variable m, F to var f and I to var I

### Example Workout
Read abalone data; assign names to columns(Gender,Length,Diameter,Height,WholeWt,ShuckedWt,ViscWt,ShellWt,Rings)
plot male and female length vs diameter; males/females should have different plot symbol
plot male and female length vs diameter; males/females should have different plot symbol plot function should be used one time


What is the difference between all(x == y) and identical(x,y) ? what are their outputs for x = 1:2, y = c(1,2)

x = 1:5; Assign names to the elements 1 = ab, 2 = bc etc;
Remove the names from x = 1:5


# Chapter 3: Matrices and Array